%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------
%

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage[document]{ragged2e}


\makeatother
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\linespread{1.07}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands

\newcommand{\resumeText}[1]{
  \large{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{0.5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\vspace{2pt}\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\AtBeginDocument{\justify}
\begin{document}


%----------HEADING-----------------
\begin{center}
    \textbf{\huge \scshape Hashem Alayan} \\ \vspace{1pt}
    \large \href{tel:+962798609212}{\underline{+962798609212}} $|$ \href{mailto:hashem.olayano@gmail.com}{\underline{hashem.olayano@gmail.com}} $|$ 
    \href{https://linkedin.com/in/hashem-alayan}{\underline{linkedin.com/in/hashem-alayan}} $|$
    \href{https://github.com/hashem78}{\underline{github.com/hashem78}}
\end{center}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.just.edu.jo/}{Jordan University of Science and Technology}}{Irbid, Jordan}
      {Bachelor of Science in Computer Engineering;  GPA: 3.81/4.0 (95\%, Excellent)}{Sep. 2018 -- Jul. 2023}   
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
\small{
    \textbf{Languages \& Frameworks}: Go \textbf{BubbleTea \& Templ}, Java \textbf{Spring, Servlets \& JSPs}, C\# \textbf{.NET} , Dart \textbf{Flutter}.
    \\
    \textbf{Back-end, Infrastructure \& Tools}: Grafana, OTEL, Loki, Terraform, Atlantis, Ansible, Puppet, Bash, Podman, Docker, Nginx, \textbf{Git}, GitHub \& GitHub Actions, MYSQL, MSSQL, JDBC, JPA.
}

\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Software Engineer | Platform \& Reliability}{Jan. 2024 -- Present}
      {Atypon Systems, A Wiley Brand - Full Time}{Amman, Jordan}
      \resumeItemListStart
       \resumeItem{
            Improved developer productivity metrics 100x by migrating our 20M LoC mono-repo flagship product Literatum from SVN (subversion) source control to Git.
        }
        \resumeItem{
            Saved our organization 1.3 million man-hours annually by cutting the compilation time of our flagship product Literatum by 80\% (from ~30 minutes to ~2 minutes) through metric-collection, caching, visualization, reporting, careful analysis and decisive action.
        }
        \resumeItem{
          Eliminated developer toil by creating a TUI (terminal user interface) in GoLang with BubbleTea to rebuild our internal deployment utility (DeployServer) resulting in 100\% reduced failure rates and deadlocks and finer grained control on deployments.
        }
      \resumeItemListEnd
    \resumeSubheading
      {Software Engineer}{Feb. 2023 -- Jan. 2024}
      {Labiba for Artificial Intelligence - Full Time}{Amman, Jordan}
      \resumeItemListStart
      \resumeItem{
        Served 35 million users across billions of requests by building scalable back-end API services with .NET 6+, awarding Labiba a contract with a major government entity in Saudia Arabia.
      }
      \resumeItem{
         Slashed 1000s in monthly costs by integrating self-hosted large language models (Falcon-50b \& LLaMa-13b) for semantic search, leveraging technologies like chromaDB and Redis, reducing dependency on costly external APIs.
      }
    \resumeItem{
        Conducted code reviews, and enforced unit testing, commit, code and linting rules in addition to static analysis through Github actions, and implemented automatic deployment schemes for our .NET 6+ / Python projects reducing the time spend on deployments for new clients by 80\% from days to hours.
    }
      \resumeItemListEnd

  \resumeSubHeadingListEnd
    


%-----------EXPERIENCE-----------------
\section{Projects}
   \resumeSubHeadingListStart
   \resumeProjectHeading
          {\href{https://englingo.com}{\textbf{Englingo}} $|$ \emph{Google Play/Apple Payments, Education, Mobile, Web, Flutter} • \href{https://englingo.com}{\underline{Website}}}{June 2024}
          \resumeItemListStart
                \resumeItem{
                    Secured \$10K in funding to build the next generation of AI infused e-Learning experience for Turkish speakers looking to learn English creating a successful MVP. Utilized Flutter, Firebase and ChatGPT to create a truly one of a kind cross platform learning SaaS.
                }
          \resumeItemListEnd
    \resumeProjectHeading
          {\href{https://github.com/KrapiOrg}{\textbf{Krapi}} $|$ \emph{Micro Services, LevelDB, Concurrency, C++, Flutter} • \href{https://youtu.be/NvcLwSh_mIw}{\underline{Demo}} • \href{https://github.com/KrapiOrg}{\underline{Source Code}}}{April 2022 -- Feb. 2023}
          \resumeItemListStart
                \resumeItem{
                    Developed a Block chain (C++) and block chain explorer implementation (Flutter), used industry standard protocols HTTP/1.1, TLS, Web Sockets and WebRTC to achieve a p2p network. Scored an A (Excellent) as my graduation project and resulted in ongoing work for a research paper.
                }
          \resumeItemListEnd
             \resumeProjectHeading      
        {\href{https://github.com/hashem78/hasha}{\textbf{Hasha}} $|$ \emph{C++, CLang, CMake, Git} • \href{https://github.com/hashem78/hasha}{\underline{Source Code}}}{Mar. 2022  -- June 2022}
          \resumeItemListStart
            \resumeItem{ Interpreted expression evaluation programming language written in modern C++ with a hand-written recursive-descent parser that supports functions, arbitrarily complex expressions and scoping.}
          \resumeItemListEnd
        \resumeProjectHeading 
    {\href{https://github.com/hashem78/aussie}{\textbf{Aussie}} $|$ \emph{Mobile/Web, Python, Selenium} • \href{https://github.com/hashem78/aussie/tree/main\#screenshots}{\underline{Demo}} • \href{https://github.com/hashem78/aussie}{\underline{Source Code}}}{Feb. 2021  -- June 2021}
          \resumeItemListStart
                \resumeItem{
                    3rd place winner in the Australian Embassy's app contest in Amman. Aimed at the MENA demographic, it curates bilingual content (Arabic \& English) about Australia. The backend boasts of a 2.2GB dataset, aggregated using Python and Selenium WebDriver scraping techniques from 100+ web sources, and is hosted on a Firebase NoSQL database.
                }
        \resumeItemListEnd
    \resumeSubHeadingListEnd

 
%-------------------------------------------
\end{document}

